Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
update data type and preamble

library(tidyverse)
```

```{r}
#| include: false
#| warning: false
#| message: false
# load data
president_polls_cleaned_data <- read.csv('../data/02-analysis_data/president_polls_cleaned_data.csv')
# transfer date to standard form
president_polls_cleaned_data$end_date <- ymd(president_polls_cleaned_data$end_date)
```

>>>>

library(tidyverse)
library(arrow)
```

```{r}
#| include: false
#| warning: false
#| message: false
# load data
president_polls_cleaned_data <- read_parquet('../data/02-analysis_data/president_polls_cleaned_data.parquet')
# transfer date to standard form
president_polls_cleaned_data$end_date <- ymd(president_polls_cleaned_data$end_date)
```
